\mythesistitleNOTSYNPOSIS \tnote[fyi]{Synopsis title is ``Generalization of Consecutive Ones Property of Binary Matrices''}

### 2012-01-16 src/030chap3.tex
Fixed a bug in chapter 2 (from last commit). Endnotes in chap 2 changed to footnotes. Tucker matrices coded. Tikz is going to be the way of the graphics in Infinite Jest.

  \noindent
  If the intersection graphs of $\cF$ and $\cP$ (a path system) are
  isomorphic, $\bI(\cF) \cong \bI(\cP)$, then the associated bijection
  $\cl: \cF \rightarrow \cP$ due to this isomorphism is called a {\em
    path labeling} of the hypergraph $\cF$.\endnote{Note that there
    are two kinds of isomorphisms here.  One is the isomorphism of
    intersection graphs on $\cF$ and $\cP$, i.e. $\bI(\cF)$ and
    $\bI(\cP)$ respectively. Second is the isomorphism between the
    hypergraphs $\cF$ and $\cP$.}

>>>>

  \noindent
  If the intersection graphs of $\cF$ and $\cP$ (a path system) are
  isomorphic, $\bI(\cF) \cong \bI(\cP)$, then the associated bijection
  $\cl: \cF \rightarrow \cP$ due to this isomorphism is called a {\em
    path labeling} of the hypergraph $\cF$.\footnote{Note that there
    are two kinds of isomorphisms here.  One is the isomorphism of
    intersection graphs on $\cF$ and $\cP$, i.e. $\bI(\cF)$ and
    $\bI(\cP)$ respectively. Second is the isomorphism between the
    hypergraphs $\cF$ and $\cP$.}
